---
title: "Trifecta of personality (Temp name)"
subtitle: "Cody's Data Science Portfolio"
output:
  html_document:
    df_print: paged
---

## Abstract

In under 250 words give a brief summary of the project so far.

### 1. Discovery and Data Preparation

Provide a one-sentence introduction with what is covered by the first deliverable along with a link to another html page that gives the details.

My motivation for this topic is I'm interested if there is a link between education, economic standing, and political standing.

My source for my initial data is Pew Research Center, (https://www.people-press.org/dataset/2015-governance-survey/), which conducted a phone survey of more that 6,000 adults and also draws on data from other surveys they've done back to 1994.
The survey size was small and could've been better but they are also drawing inferences from previous surveys to better extrapolate from the data.

```{r}

library("haven")
path = file.path("C:", "Rdata", "Governance 2015.public.sav")
dataset = read_sav(path)

colnames(dataset)
```

The variables of the data set are mostly understandable and comes with a readme.txt and a topline.pdf that you can further look at when going to the link.


```{r}
library(tidyverse)
ggplot()

```

This 

### 2. Model Planning and Building

Coming soon...

### 3. Results and Operationalization

Coming soon...

